\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-11-01 OaklandSubmission/related.tex
nits

\tool falls into the category of frameworks that compile high level languages to \mpc protocols. We discuss other such frameworks next.
%Existing \mpc tools work with either a high or a low level desciption of the functionalities to be implemented securely.
 %\end{enumerate}
%\noindent\textbf{Generating \mpc protocols.}
%There has been vast literature on the generation of \mpc protocols. These works all provide tools at various levels of abstraction that help a programmer generate cryptographic protocols for various functionalities. These levels can be classified as follows: 
%Examples of tools in the former category include the following: 
Fairplay's Secure Function Definition Language (SFDL)~\cite{fairplay,fairplaymp} and CBMC-GC~\cite{cbmcgc} compile C or Pascal like programs into boolean circuits that are then evaluated using garbled circuits~\cite{yao}.
ObliVM~\cite{oblivm} protects access patterns using an oblivious RAM~\cite{oram1,oram2} and also uses garbled circuits for compute.
In Secure Multiparty Computation Language (SMCL)~\cite{smcl},  Java like programs are compiled into arithmetic circuits that are then evaluated using the VIFF framework~\cite{viff}. Wysteria~\cite{wysteria} compiles  programs into boolean circuits and uses a GMW-based backend~\cite{choi,gmw}. 
 Mitchell et al.~\cite{lambdaps} allow the user to select between Shamir's secret sharing~\cite{sss} and fully homomorphic encryption~\cite{gentry}.  Unlike \tool, all these tools use either an arithmetic backend or a boolean backend but not a combination of both.

>>>>

\tool falls into the category of frameworks that compile high level languages to \mpc protocols. We discuss other such frameworks next.
%Existing \mpc tools work with either a high or a low level desciption of the functionalities to be implemented securely.
 %\end{enumerate}
%\noindent\textbf{Generating \mpc protocols.}
%There has been vast literature on the generation of \mpc protocols. These works all provide tools at various levels of abstraction that help a programmer generate cryptographic protocols for various functionalities. These levels can be classified as follows: 
%Examples of tools in the former category include the following: 
Fairplay's Secure Function Definition Language (SFDL)~\cite{fairplay,fairplaymp} and CBMC-GC~\cite{cbmcgc} compile C or Pascal like programs into boolean circuits that are then evaluated using garbled circuits~\cite{yao}.
ObliVM~\cite{oblivm} protects access patterns using an oblivious RAM~\cite{oram1,oram2} and also uses garbled circuits for compute.
In Secure Multiparty Computation Language (SMCL)~\cite{smcl},  Java
like programs are compiled into arithmetic circuits that are then
evaluated using the VIFF
framework~\cite{viff}. Wysteria~\cite{wysteria} enables programmers to
write $n$-party mixed-mode programs that combine local, per-party
computations with secure computations. It compiles secure
computations to
boolean circuits and uses a GMW-based backend~\cite{choi,gmw}.
 Mitchell et al.~\cite{lambdaps} allow the user to select between
 Shamir's secret sharing~\cite{sss} and fully homomorphic
 encryption~\cite{gentry}.  Unlike \tool, all these tools use either
 an arithmetic backend or a boolean backend but not a combination of
 both.
